Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-08-02 supCLT.tex
change supCLT.tex

%---The preamble----------------------

@@

%\usepackage[backref=section]{hyperref}

@@

%\usepackage[nobysame]{amsrefs}

@@

%---Top matter------------------------------

@@

\address
    {Yan-Xia Ren
    \\ LMAM School of Mathematical Sciences \& Center for Statistical Science
    \\ Peking University
    \\ Beijing, P. R. China, 100871}

@@

\address
    {Renming Song
    \\ Department of Mathematics
    \\ University of Illinois at Urbana-Champaign
    \\ Urbana, IL 61801, USA}

@@

\address
    {Zhenyao Sun
    \\ School of Mathematical Sciences
    \\ Peking University
    \\ Beijing, P. R. China, 100871}

@@

\address
    {Jianjie Zhao
    \\ School of Mathematical Sciences
    \\ Peking University
    \\ Beijing, P. R. China, 100871}

@@

Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$. Let $\psi$ be a branching mechanism which is close to a function of the form $\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense. In this paper, we study asymptotic behaviors of
$(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$. For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$. Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.

@@

%---Contents-----------------------

@@

@@

    = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
    \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),

@@

\begin{equation} \label{eq: honogeneou branching mechanism}

@@

    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb R_+,

@@

$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure
of $\psi$.

@@

       We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$
on a measurable space $(\Omega, \mathcal{F})$
       is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, 
     or a $(\xi, \psi)$ superprocess,  
       if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have

@@

    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),

@@

	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.

@@

    Recently, there have been quite a few papers on laws of large numbers for superdiffusions. In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established. The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost},
    followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost} under different settings.
    For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.

   The strong law of large numbers for the super-OU process $X$ can be stated as follows:
    Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$,
    for every Lebesgue-a.\/e. continuous bounded non-negative function $f$ on $\mathbb R^d$,
    we have
    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f, \varphi\rangle $,
    where $H_\infty$ is the limit of the martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and
$\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
    See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.

    In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above.
    Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
    We want to find
    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
%\[
$
 %   \frac{\langle f, X_t \rangle -G_t}{F_t}
    (\langle f, X_t \rangle -G_t)/F_t
%\]
$
    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
    It turns out that the statements of the CLT's are different in three regimes
    depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
    Note that, in the setting of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.

    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
   See   \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for %supercritical Galton-Watson processes,
   supercritical Galton-Watson processes (GW processes),
    \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type %Galton-Watson processes,
    GW processes
    \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
%In \cite{AdamczakMilos2015CLT}, Adamczak and Mi\l{}o\'s proved some spatial central limit theorems for   supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Mi\l{}o\'s proved some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
Some spatial central limit theorems for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
    These two papers made connections between the CLT and  the branching rate regimes.
%In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition.
Some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition were established in \cite{RenSongZhang2014Central}.
Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
%In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}, Ren, Song and Zhang also established a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms
were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
    The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.

There are also many limiting theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moments.
Heyde \cite{Heyde1971Some} established a central limit type  theorem 
%for supercritical Galton-Watson process when the offspring distribution
for supercritical GW processes when the offspring distribution
belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
and   proved that the limit law is  a stable law. Similar results  for supercritical multi-type 
%Galton-Watson processes and supercritical  continuous time branching processes, 
GW processes and supercritical  continuous time branching processes, 
under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
were given in Asmussen \cite{Asmussen76Convergence}.
Recently,   Marks and Milo\'s \cite{MarksMilos2018CLT}
%considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes 
considered the limit behavior of supercritical branching OU processes
with a special stable branching law.
	They established some spatial central limit theorems in the small and critical branching rate regimes,
    but they did not prove any central limit theorem type result in the large branching rate regime.
    We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.

@@

\subsection{Main results}
\label{sec: main results}{}

We will always assume that the following assumption holds.
\begin{asp}
\label{asp: Greys condition}
	The branching mechanism satisfies Grey's condition, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
\end{asp}
    For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition},
	the \emph{extinction event}
	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
    In fact,
%\begin{equation}
$
    \mathbb{P}_{\mu} (D)
    = e^{-\bar v \|\mu\|},
%    \quad \mu\in \mathcal M(\mathbb R^d),
%\end{equation}
$ for $\mu\in \mathcal M(\mathbb R^d)$,
    where
%\[
$
	\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
%\]
$
	is the largest root of $\psi$.

    Denote by $\Gamma$ the gamma function.
For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
    In this paper, we will also assume the following:
\begin{asp}
\label{asp: branching mechanism}
    There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{equation}
\label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
\end{equation}
	for some $\delta > 0$.
\end{asp}
	We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
	In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.

@@

    Assumption \ref{asp: branching mechanism} says that
 there exist constants $\eta>0$ and $\beta > 0$
    such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
    In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$
    takes the form of
	$-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
	It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption
	\ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the
	$L \log L$ condition, i.e.,
%\[
$
	\int_{(1,\infty)} y\log y~\pi(dy) < \infty.
%\]
$
    This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.

    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel functions on $\mathbb R^d$.
    We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
    Define
\begin{equation}
\label{eq: meansemigroup}
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}
        The limiting behavior of the super-OU process is closely related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.

    We now recall some basic spectral properties of $(P_t)_{t\geq 0}$ from \cite{MetafunePallaraPriola2002Spectrum}.
       It is known that the OU process $\xi$ has an invariant density
\label{invariantdensity}
    \varphi(x)dx
    :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$.
        Then $L^2(\varphi)$ is a Hilbert space with inner product
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
       Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
    For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$,
    $p!:= \prod_{k= 1}^d p_k!$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The \emph{Hermite polynomials} are defined by
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    p \in \mathbb{Z}_+^{d}.
It is known that $(P_t)_{t\geq 0}$
       is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum
        $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then

>>>>

% * The preamble

@@

@@

@@

% * Top matter

@@

\address{
  Yan-Xia Ren \\
  LMAM School of Mathematical Sciences \& Center for Statistical Science \\
  Peking University \\
  Beijing, P. R. China, 100871}

@@

\address{
  Renming Song \\
  Department of Mathematics \\ 
  University of Illinois at Urbana-Champaign \\ 
  Urbana, IL 61801, USA}

@@

\address{
  Zhenyao Sun \\ 
  School of Mathematical Sciences \\ 
  Peking University \\ 
  Beijing, P. R. China, 100871}

@@

\address{
  Jianjie Zhao \\ 
  School of Mathematical Sciences \\ 
  Peking University \\ 
  Beijing, P. R. China, 100871}

@@

  Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$. 
  Let $\psi$ be a branching mechanism which is close to a function of the form $\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense. 
  In this paper, we study asymptotic behaviors of $(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$. 
  For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$. 
  Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes: 
  the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; 
  the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; 
  and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.

@@

% * Contents

@@

% ** Motivation

@@

  = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x)
  , \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),

@@

  \label{eq: honogeneou branching mechanism}

@@

  - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy)
  , \quad  z \in \mathbb R_+,

@@

$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.

@@

We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ on a measurable space $(\Omega, \mathcal{F})$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a $(\xi, \psi)$ superprocess, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have

@@

  = e^{-\langle V_tf, \mu \rangle}
  , \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),

@@

	= \Pi_x [f(\xi_t)]
  , \quad x\in \mathbb R^d, t\geq 0.

@@

Recently, there have been quite a few papers on laws of large numbers for superdiffusions. 
In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established. 
The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost}, followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines, KouritzinRen2014A-strong, LiuRenSong2013Strong, Wang2010An-almost} under different settings.
For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.

The strong law of large numbers for the super-OU process $X$ can be stated as follows:
Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, for every Lebesgue-a.\/e. continuous bounded non-negative function $f$ on $\mathbb R^d$, we have $\lim_{t\to\infty} e^{-\alpha t} \langle f, X_t\rangle =H_\infty\langle f, \varphi\rangle $, where $H_\infty$ is the limit of the martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.

In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above.
Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
We want to find $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
%\[
$
% \frac{\langle f, X_t \rangle -G_t}{F_t}
(\langle f, X_t \rangle -G_t)/F_t
% \]
$
converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for a large class of functions $f$.
It turns out that the statements of the CLT's are different in three regimes depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: 
the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; 
the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; 
and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. 
Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
Note that, in the setting of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.

There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
See   \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for %supercritical Galton-Watson processes,
supercritical Galton-Watson processes (GW processes),
\cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type %Galton-Watson processes,
GW processes
\cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
% In \cite{AdamczakMilos2015CLT}, Adamczak and Mi\l{}o\'s proved some spatial central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Mi\l{}o\'s proved some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
Some spatial central limit theorems for   supercritical branching OU processes with binary branching mechanism were proved in \cite{AdamczakMilos2015CLT} and some spatial central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition were proved in \cite{Milos2012Spatial}.
These two papers made connections between the CLT and  the branching rate regimes.
% In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition.
Some spatial central limit theorems for supercritical super-OU  processes with branching mechanisms satisfying only asecond moment condition were established in \cite{RenSongZhang2014Central}.
Moreover, compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
% In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}, Ren, Song and Zhang also established a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
Since then, a series of spatial central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms were proved in \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central}.
The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.

There are also many limiting theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moments.
Heyde \cite{Heyde1971Some} established a central limit type  theorem 
% for supercritical Galton-Watson process when the offspring distribution
for supercritical GW processes when the offspring distribution
belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$, and proved that the limit law is  a stable law. 
Similar results  for supercritical multi-type 
% Galton-Watson processes and supercritical  continuous time branching processes, 
GW processes and supercritical  continuous time branching processes, 
under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution, were given in Asmussen \cite{Asmussen76Convergence}.
Recently, Marks and Milo\'s \cite{MarksMilos2018CLT}
% considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes 
considered the limit behavior of supercritical branching OU processes
with a special stable branching law.
They established some spatial central limit theorems in the small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.

@@

% ** Main results
\subsection{Main results}
\label{sec: main results}{}
We will always assume that the following assumption holds.
\begin{asp}
\label{asp: Greys condition}
The branching mechanism satisfies Grey's condition, i.e., there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
\end{asp}
For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event} $D :=\{\exists t\geq 0,~\text{s.t.}~ \|X_t\| =0 \}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
In fact,
%\begin{equation}
$
\mathbb{P}_{\mu} (D)
= e^{-\bar v \|\mu\|},
% \quad \mu\in \mathcal M(\mathbb R^d),
% \end{equation}
$ 
for $\mu\in \mathcal M(\mathbb R^d)$,
where
% \[
$
\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
% \]
$
is the largest root of $\psi$.

Denote by $\Gamma$ the gamma function.
For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
In this paper, we will also assume the following:
\begin{asp}
  \label{asp: branching mechanism}
  There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
  \begin{align}
    \label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
  \end{align}
	for some $\delta > 0$.
\end{asp}
We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
In the reminder of the paper, we will always use $\eta$ and $\beta$ to denote the constants in Assumption  \ref{asp: branching mechanism}.

@@

Assumption \ref{asp: branching mechanism} says that there exist constants $\eta>0$ and $\beta > 0$ such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of $-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ condition, i.e.,
%\[
$
\int_{(1,\infty)} y\log y~\pi(dy) < \infty.
% \]
$
This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.

Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel functions on $\mathbb R^d$.
We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
Define
\begin{align}
  \label{eq: meansemigroup}
  P^{\alpha}_t f(x)
  :=
  e^{\alpha t} P_t f(x) 
  = \Pi_x [e^{\alpha t}f(\xi_t)]
  , \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{align}
It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}
  \mathbb{P}_{\mu}[\langle f, X_t \rangle]
  = \langle P^\alpha_t f, \mu \rangle,
  \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}
The limiting behavior of the super-OU process is closely related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.
